Capstone Movielens Report

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: calc_UMGY_effect_RMSE.cv.

#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) Function {#func.calc_UMGY_effect_MSE.cv}
\

@@

The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is shown below:
```{r eval=FALSE}
calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
  start <- put_start_date()
  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
  })
  put_end_date(start)
  put_log1("Function: calc_UMGY_effect_MSE.cv
Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
           CVFolds_N)

@@

::: {.noteblock data-latex=""}
The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) script on _GitHub_.
:::
:::

@@

Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

@@

@@

The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is shown below:
```{r eval=FALSE}
```

>>>>

#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) Function {#func.calc_UMGY_effect_MSE.cv}
\

@@

The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) function is shown below:
```{r eval=FALSE}
calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
  start <- put_start_date()
  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
  })
  put_end_date(start)
  put_log1("Function: calc_UMGY_effect_MSE.cv
Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
           CVFolds_N)

@@

::: {.noteblock data-latex=""}
The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) script on _GitHub_.
:::
:::

@@

@@

```{r eval=FALSE}
cv.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMGY_effect)
```
:::

@@

The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is shown below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
           CVFolds_N, 
           UMGY_effect_RMSE)

  UMGY_effect_RMSE
}
```
